\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-05-22 paper/ms.tex
tiny changes to abstract

\newcommand{\ktwo}{{\it K$\mathit{2}$}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}
\newcommand{\code}{\texttt}
\newcommand{\clh}[1]{\textcolor{red}{ \textbf{***CLH: #1 ***}}}
\newcommand{\ze}[1]{\textcolor{blue}{ \textbf{***CLH: #1 ***}}}
\newcommand{\gb}[1]{\textcolor{green}{ \textbf{***CLH: #1 ***}}}

@@

\begin{abstract}
    The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
    These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet
    candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as
    aperture choice and background correction methods. These assumption are valid for the majority of targets,
    but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw
    Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their
    particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
    Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic
    rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open
    source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface
    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is
    simple and quick to create corrected time-series photometry from raw pixel data from any of these
    missions and perform many common light curve corrections, including correcting for K2 motion using
    the SFF method and correcting for correlated trends using cotrend basis vectors.
    \lightkurve~ is open source and provides an excellent learning tool for any users wanting
    to get to started with Kepler data.
\end{abstract}

>>>>

\newcommand{\ktwo}{{\it K$\mathit{2}$}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}
\newcommand{\clh}[1]{\textcolor{red}{ \textbf{***CLH: #1 ***}}}
\newcommand{\ze}[1]{\textcolor{blue}{ \textbf{***CLH: #1 ***}}}
\newcommand{\gb}[1]{\textcolor{green}{ \textbf{***CLH: #1 ***}}}

@@

\begin{abstract}
    The \kepler~ and \ktwo~ missions has provided the astronomy community with light curves of more than 400,000 objects.
    These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet
    candidates. However, light curves processed by the Kepler pipeline have built-in, fixed assumptions, such as
    aperture choice and background correction methods. These assumptions are valid for the majority of targets,
    but for certain science cases a bespoke analysis may be more valuable. Performing custom photometry with the raw
    \kepler~ data has many benefits. Working with the raw data allows users to mitigate systematics for their
    particular science case, (such as the \kepler~ Rolling band) and verify the aperture selected by the pipeline.
    Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic
    rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open
    source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface
    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve, it is
    simple and quick to create corrected time-series photometry from raw pixel data from any of these
    missions and perform many common light curve corrections, including correcting for spacecraft motion induced
    noise using the self-flat-field method and correcting for correlated trends using cotrend basis
    vectors. \lightkurve~ is open source and provides an excellent learning tool for any users wanting
    to get to started with Kepler data.
\end{abstract}
